\documentclass[10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[margin=3cm]{geometry}
\usepackage[usenames,dvipsnames]{color}
\usepackage{array}
\usepackage[colorlinks=true, urlcolor=MidnightBlue]{hyperref}
\usepackage{fancyhdr}
\usepackage{fixltx2e} % \textsubscript
\usepackage{layout}

\signature{Jamie Macdonald}

%%% Measurements %%%
% \topmargin=-0.3in
\oddsidemargin=0in
\evensidemargin=0in
\textwidth=6.5in
\marginparwidth=0.5in
% \headheight=0pt
\headsep=0pt
\textheight=670pt

% \title{JAMIE A. MACDONALD}
% \author{\href{mailto:jamie.alban@gmail.com}{jamie.alban@gmail.com}\\(613) 583-7654\\2251 Fife Cres.\\Ottawa, ON}
% \date{}
\address{\href{mailto:jamie.alban@gmail.com}{jamie.alban@gmail.com}\\(613) 583-7654\\2251 Fife Cres.\\Ottawa, ON}

\begin{document}
	\begin{letter}{\href{mailto:candrei@developmentgateway.org}{candrei@developmentgateway.org} \\Catalin Andrei, Director of IT \\ Development Gateway}
		\opening{Hi, Catalin!}
		I have attached my résumé to the following page of this pdf. Please consider this an application for a software development position at Development Gateway.

		I am about to graduate from the Mathematics and Engineering: Computer and Communication Systems from Queen's University, Kingston, Canada, and I am looking for fulltime employment in the coming new year.

		I am a believer that simple, accessible information technology can help tip the scales of development work by empowering local populations with the tools to rule their future. I am furthermore impressed by the initiative from your organization in focussing on crowdsourcing and geocoding of aid information with AidData: it truly aims to empower donors and organizations to better serve people on the ground.

		I am especially motivated by working toward positive social impact, I advocate Free Software, activism, and would direct my skills to these endeavors foremostly.

		My mathematical background spans many applied fields (see attached résumé), and I strive to apply these technical skills in my software. In particular, my foundation in statistics aided my work in maintaining a visualization/charting engine for IBM last summer and my probability skills often help to formally assess the efficacy of algorithms and software solutions. My application interests include social networks, alternative crypto-currencies, human-computer interaction, distributed systems, data visualization.

		I am proficient in Java, and more recently clientside and serverside Javascript, but have prowess and experience in many other languages. 

		I hope that you find me a good fit for your organization, and I look forward to talking to you further about this opportunity!

		\closing{Sincerely,}
	\end{letter}
\end{document}